Report - Latest Rodent Data

### 2018-02-16 index.Rmd

data = compile_forecasts()
ensemble = dplyr::filter(data, level == 'Controls', model == 'Ensemble', date == max(date))
sp_predictions = get_sp_predicts(ensemble, 'Contols', lead_time = 1)
sp_predict = plot_species_forecast(sp_predictions,
            title=paste0(sp_predictions$forecast_date[2], ": Control plots"))

>>>>

data = compile_forecasts()
ensemble = dplyr::filter(data, level == 'Controls', model == 'Ensemble', date == max(date))
sp_predictions = get_sp_predicts(ensemble, 'Controls', lead_time = 1)
sp_predict = plot_species_forecast(sp_predictions,
            title=paste0(sp_predictions$forecast_date[2], ": Control plots"))

### 2018-02-16 profiles.Rmd

              "![](rodent_pictures/color_pictures/OL.png)",
              "![](rodent_pictures/color_pictures/OT.png)",

@@

              "![](rodent_pictures/color_pictures/RF.png)",
              "![](rodent_pictures/color_pictures/RM.png)",
              "![](rodent_pictures/color_pictures/RO.png)",
              "![](rodent_pictures/color_pictures/SF.png)",
              "![](rodent_pictures/color_pictures/SH.png)",
              "![](rodent_pictures/color_pictures/SO.png)"), 

>>>>

              "![](rodent_pictures/color_pictures/OL.JPG)",
              "![](rodent_pictures/color_pictures/OT.JPG)",

@@

              "![](rodent_pictures/color_pictures/RF.jpg)",
              "![](rodent_pictures/color_pictures/RM.jpg)",
              "![](rodent_pictures/color_pictures/RO.JPG)",
              "![](rodent_pictures/color_pictures/SF.jpg)",
              "![](rodent_pictures/color_pictures/SH.jpg)",
              "![](rodent_pictures/color_pictures/SO.jpg)"), 

### 2018-02-16 report.Rmd

# get most recent rodent data
rodents = abundance("repo", shape='flat', level='treatment')
most_recent_period = max(rodents$period)
observed = dplyr::filter(rodents, period == most_recent_period, treatment=='control')

>>>>

# get most recent rodent data
rodents = abundance("repo", shape='flat', level='treatment', length='longterm')
most_recent_period = max(rodents$period)
observed = dplyr::filter(rodents, period == most_recent_period, treatment=='control')
